An overview of the oolong package.

### 2020-06-14 overview_gh.Rmd

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` and LDA/CTM models from `topicmodels`.

>>>>

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels` and Biterm Topic Models from `BTM`.
